Solving Collective Spin Hamiltonians with Decoherence

### 2018-10-03 soc_squeezing/cumulant_expansions.tex
realized that calculation of the product of two operators was not actually completed... it now is

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} \sum_{\p{\v\rho;\v r}}
  \sum_{\p{\v\ell;\v m,\v n,\v r,\v\rho}}
  f_{\v m\v n\v r} g_{\v\rho} \v\eta_{\v\rho} c_{\v\ell\v\rho} P_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the sums over $\p{\v\rho;\v r}$ and
$\p{\v\ell;\v m,\v n,\v r,\v\rho}$ respectively denote sums over all
values of $\v\rho$ and $\v\ell$ with the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \abs{\set{\ell^\mu_a}}
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv \p{ N - \abs{\v\ell} }_ {\sum_{\mu,\nu}\rho^{\mu\nu}_0},
\end{align}
with $\abs{\v\ell}=\sum_\mu\p{m_\mu+n_\mu}-s$ equal to the number of
elements in $\v\ell$, accounts for the multiplicity of terms which are
equivalent up to a permutation of indices involving the identity
operators in \eqref{eq:Q_K_rho_simp}.

For clarity, we note here that all indices on
$m_\mu,n_\mu,r_{\mu\nu},\rho^{\mu\nu}_\kappa,\eta_{\mu\nu\kappa}$ and
the upper index on $\ell^\mu_a$ take on the same values as the indices
on elements $\sigma_\mu$ of some complete basis for single-spin
operators; of these, only the last index ($\kappa$) on
$\rho^{\mu\nu}_\kappa,\eta_{\mu\nu\kappa}$ ever matches the index for
the identity element $\sigma_0\equiv\1$.  The lower index on
$\ell^\mu_a$ indexes the $a$-th spin acted on by a $\sigma_\mu$
operator in each term of \eqref{eq:SS_simp}.

>>>>

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} \sum_{\p{\v\rho;\v r}}
  \sum_{\p{\v\ell;\v m,\v n,\v r,\v\rho}}
  f_{\v m\v n\v r} g_{\v\rho} \v\eta_{\v\rho} c_{\v\ell\v\rho} \S_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the sums over $\p{\v\rho;\v r}$ and
$\p{\v\ell;\v m,\v n,\v r,\v\rho}$ respectively denote sums over all
values of $\v\rho$ and $\v\ell$ with the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \ell_\mu
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv \p{ N - \sum_\kappa\ell_\kappa }_{\sum_{\mu,\nu}\rho^{\mu\nu}_0},
\end{align}
accounts for the multiplicity of terms which are equivalent up to a
permutation of indices involving the identity operators in
\eqref{eq:Q_K_rho_simp}.  For clarity, we note here that all indices
on
$m_\mu, n_\mu, r_{\mu\nu}, \rho^{\mu\nu}_\kappa, \eta_{\mu\nu\kappa},
\ell_\mu$ take on the same values as the indices on elements
$\sigma_\mu$ of some complete basis for single-spin operators; of
these, only the last index ($\kappa$) on
$\rho^{\mu\nu}_\kappa,\eta_{\mu\nu\kappa}$ ever matches the index for
the identity element $\sigma_0\equiv\1$.
